\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.85]{geometry}
\usepackage{ltablex}
\keepXColumns         
\setlength\LTpre{8pt} 
\setlength\LTpost{8pt}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\hypersetup{
    hidelinks,
    pdfcreator={LaTeX},
    pdfproducer={LaTeX},
    breaklinks=true
}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Muhammad Saad Ashraf} \\[7.5pt]
Islamabad, Pakistan \\
\href{https://github.com/saad1551}{Github: saad1551}\hspace{1em}
\href{https://linkedin.com/in/saadashraf380715222}{Linkedin: saad1551}\hspace{1em}
\href{mailto:mashraf.bese22seecs@seecs.edu.pk}{Email: mashraf.bese22seecs@seecs.edu.pk}\hspace{1em}
Phone: +92 307 5777194 \\
\end{tabularx}





%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Enthusiastic Software Engineering student focused on solving complex problems, developing scalable systems, and exploring innovative areas of Computer Science research.


\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2022 - present & Bachelor's (Software Engineering) at \textbf{NUST Islamabad} \hfill \normalsize (CGPA: 3.41/4.0) \\

2020 - 2022 & Intermediate at \textbf{Adamjee Science College, Karachi} \hfill \normalsize (91.8\%) \\

2018 - 2020 & Matriculation at \textbf{The Educator's} \hfill \normalsize (87.5\%) \\
\end{tabularx}


\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{} l X @{} }
% \textbf{Exec. Web \& IT, NUST Olympiad} & \hfill Dec 2023 – Feb 2024 \\
% \multicolumn{2}{@{}p{\linewidth}@{}}{
% Built the MERN stack website for NUST’s flagship event in a fast-paced team setting.
% } \\[5pt]

% \textbf{Deep Learning Research Intern, TUKL DLL SEECS} & \hfill Jun 2024 – Nov 2024 \\
% \multicolumn{2}{@{}p{\linewidth}@{}}{
% Worked on EEG classification and explainable AI models and created a chatbot for querying 600+ EEG recordings with the ability to append more data.
% } \\[5pt]

% \textbf{Software Eng. Intern, Proto IT Consultants} & \hfill Nov 2024 – Feb 2025 \\
% \multicolumn{2}{@{}p{\linewidth}@{}}{
% Maintained 30+ scrapers collecting 300K+ events. Built backends for a major AI products.
% } \\[5pt]

% \textbf{Software Engineer, Pinkfly} & \hfill Feb 2025 – June 2025 \\
% \multicolumn{2}{@{}p{\linewidth}@{}}{
% Developing backend for a ride-hailing app and building RAG pipelines to automate in-app support.
% } \\

\textbf{Bazaar Technologies} \\[3pt]

\textbf{Engineering Trainee} & \hfill August 2025 – April 2026 \\
\multicolumn{2}{@{}p{\linewidth}@{}}{
\begin{itemize}
    \item Contributed to the development of Bazaar Pro Portal (portal.bazaarpro.co) which serves as the platform for businesses to put in their demands in order to get a quotation from Bazaar.
    \item Rebuilt the card payment feature by integrating with HBL and Cybersource, improving payment reliability, reducing payment failures to near 0\%\ and eliminating chargebacks.
    \item Eliminated security flaws in existing APIs that could have exposed sensitive user data.
    \item Integrated FBR digital invoicing via WebDNAWorks, ensuring regulatory compliance and enabling legal, automated invoice reporting.
\end{itemize}
} \\[6pt]

\textbf{Engineering Intern} & \hfill June 2025 – August 2025 \\
\multicolumn{2}{@{}p{\linewidth}@{}}{
Worked with the Finance squad and gained experience with payment flows and complex microservice architectures.
\begin{itemize}
    \item Made refunds for card payments instant via a wallet-first approach; 47\% of customers retained funds in their wallet.
    \item Integrated a new payment gateway (JazzCash) into the mobile app, resulting in an 11\% increase in digitally paid orders.
    \item Migrated microservices to the latest stable versions of Java and Spring Boot.
\end{itemize}
} \\[5pt]


\end{tabularx}

\section{Research Experience}

\begin{tabularx}{\linewidth}{ @{} l X @{} }

\textbf{Deep Learning Research Intern, TUKL DLL SEECS} & \hfill Jun 2024 – Nov 2024 \\
\multicolumn{2}{@{}p{\linewidth}@{}}{
Worked on EEG classification and explainable AI models and a chatbot for querying 600+ EEG recordings with the ability to append more data.
\begin{itemize}
    \item Conducted a thorough literature review of existing techniques for EEG classification through deep neural networks.
    \item Researched different explainability techniques and applied LIME, SHAP and Grad-CAM to EEG data.
    \item Made a chatbot using Retrieval Augmented Generation to query statistics from EEG recordings in natural language.
\end{itemize}
    
} \\[5pt]

\textbf{Undergraduate Research Collaborator, TUKL DLL SEECS} & \hfill May 2025 – Present \\
\multicolumn{2}{@{}p{\linewidth}@{}}{
Working on my final year project 'Adaptive Web Interaction: Leveraging Reinforcement Learning for Comprehensive and on natural language report generation from EEG recordings 
\begin{itemize}
    \item Training agents based on small language models for autonomous web navigation using on-policy reinforcement learning.
    \item Created a web extension in which language models can be integrated and actions can be taken on the user's browser following a natual language prompt given by the user.
\end{itemize}
    
} \\[5pt]

\end{tabularx}




%Experience



%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}X@{} }
\textbf{Search Engine} \hfill \href{https://github.com/saad1551/SearchEngine}{[GitHub]} \\
Built a large-scale search engine indexing 110k+ articles, experimenting with various search \\
algorithms from the academic literature and implementing barrelling techniques described in \\
The Anatomy of a Large-Scale Hypertextual Web Search Engine (Brin \&\ Page, 1998). \\[3.75pt]

\textbf{V-Therapist} \hfill \href{https://github.com/saad1551/psychologist-language-model}{[GitHub]} \\
Built a virtual psychologist using memory enhancement techniques on small language models. \\
Carried out research on the possible memory enhancement techniques and eventually went \\
with vector databases which gave the best performance. \\[3.75pt]

\textbf{FairGig} \hfill \href{https://fairgig.online}{[Live]} \\
Microservices-based gig worker rights platform (SOFTEC 2026) with 7 backend services (FastAPI + Express), \\
React frontend, LLM-powered shift logging, vision-based verification, and statistical anomaly detection. \\[3.75pt]

\textbf{Web-Sense} \hfill \href{https://github.com/saad1551/final-year-project}{[GitHub]} \\
An ongoing research project, also my senior year project, \\
in which we are training small language models \\
using reinforcement learning to effectively and reliably perform the task of web navigation. \\
Researching different on-policy RL techniques to use the available \\
datasets in improving the performance of these models. \\[3.75pt]

\textbf{Scored} \hfill \href{https://github.com/saad1551/cricketScoreboard}{[GitHub]} \\
A complete cricket scoring system along with a win predictor consistent with all the complex \\
rules and playing conditions of the game. The win predictor was based on previous statistics \\
of the players taking part in the game.\\[3.75pt]

\textbf{Book Reviews Backend} \hfill \href{https://github.com/saad1551/expressBookReviews}{[GitHub]} \\
NodeJS + Express app with auth and review system using middlewares. \\[3.75pt]

\textbf{EEG Chatbot} \hfill \href{https://github.com/saad1551/eeg-chatbot}{[GitHub]} \\
LangChain-based bot to query EEG statistics and specifics via natural language. \\[3.75pt]

\textbf{Dastkaar E-commerce} \hfill \href{https://github.com/saad1551/web-engineering-project-backend}{[GitHub]} \\
Platform enabling rural women to sell handmade goods online. \\[3.75pt]

% \textbf{Digit Recognition} \hfill \href{https://github.com/saad1551/DeepLearning}{[GitHub]} \\[3.75pt]
% Classified MNIST digits using VGG16 with 96\% test accuracy. \\



\textbf{Plant Shop Frontend} \hfill \href{https://saad1551.github.io/e-plantShopping/}{[Live]} \\
ReactJS store with cart, Redux-based state, and product management. \\[3.75pt]

\textbf{Conference Planner} \hfill \href{https://saad1551.github.io/react-conference-planner-app/}{[Live]} \\
ReactJS + Redux app to plan events across multiple categories. \\








% \textbf{Cricket Shots Classifier} & \hfill \href{https://github.com/saad1551/DeepLearning}{[GitHub]} \\[3.75pt]
% VGG16-based model to detect cricket shots (88\% accuracy). \\

% \textbf{Disaster Tweets} & \hfill \href{https://www.kaggle.com/code/saadashraf88/nlp-disaster}{[Kaggle]} \\[3.75pt]
% TensorFlow model to classify tweets as real disaster or not. \\
\end{tabularx}



\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming languages: &  \normalsize{Javascript, Python, C, C++, Java, Kotlin} \\
Backend: &  \normalsize{NodeJS + ExpressJS, Django, Springboot} \\
Frontend:  &  \normalsize{ReactJS} \\
Databases:  &  \normalsize{MongoDB, MySQL, PostgreSQL, PostGIS, SQLite, Redis} \\
DevOps:  &  \normalsize{Docker, Kubernetes, CI/CD} \\
\end{tabularx}




% \section{Work Experience}

% \begin{tabularx}{\linewidth}{ @{} l X @{} }
% % \textbf{Exec. Web \& IT, NUST Olympiad} & \hfill Dec 2023 – Feb 2024 \\
% % \multicolumn{2}{@{}p{\linewidth}@{}}{
% % Built the MERN stack website for NUST’s flagship event in a fast-paced team setting.
% % } \\[5pt]

% \textbf{Deep Learning Research Intern, TUKL DLL SEECS} & \hfill Jun 2024 – Nov 2024 \\
% \multicolumn{2}{@{}p{\linewidth}@{}}{
% Worked on EEG classification and explainable AI models and created a chatbot for querying 600+ EEG recordings with the ability to append more data.
% } \\[5pt]

% % \textbf{Software Eng. Intern, Proto IT Consultants} & \hfill Nov 2024 – Feb 2025 \\
% % \multicolumn{2}{@{}p{\linewidth}@{}}{
% % Maintained 30+ scrapers collecting 300K+ events. Built backends for a major AI products.
% % } \\[5pt]

% % \textbf{Software Engineer, Pinkfly} & \hfill Feb 2025 – June 2025 \\
% % \multicolumn{2}{@{}p{\linewidth}@{}}{
% % Developing backend for a ride-hailing app and building RAG pipelines to automate in-app support.
% % } \\

% \textbf{Software Engineer Intern, Bazaar Technologies} & \hfill Jun 2025 – Present \\
% \multicolumn{2}{@{}p{\linewidth}@{}}{
% Worked with the Finance squad and gained experience with payment flows and complex microservice architectures.
% \begin{itemize}
%     \item Made refunds for card payments instant via wallet-first approach. 47\%\ customers retained the money in their wallet.
%     \item Integrated a new payment gateway into the mobile app, resulting in an 11\%\ increase in digitally paid orders.
%     \item Migrated microservices to the latest stable versions of Java and Springboot
% \end{itemize} 
% } \\[5pt]

% \end{tabularx}










%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Certifications}
\begin{tabularx}{\linewidth}{@{}X r@{}}
Developing Backend Apps with Node JS and Express by \textbf{IBM} & 2024 \\

Developing Frontend Apps with React by \textbf{IBM} & 2024 \\

Machine Learning Specialization by \textbf{DeepLearning.AI, Stanford University} & 2024 \\

Deep Learning Specialization by \textbf{DeepLearning.AI, Stanford University} & 2024 \\
\end{tabularx}

\section{Extra-Curricular Activities}
\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{Marketing Executive, Google Developer Student Club (NUST)} 
& Sep 2024 -- May 2025 \\
\multicolumn{2}{@{}X@{}}{Successfully marketed multiple events and gathered audiences of 200--500 people.} \\[6pt]

\textbf{Team Member, NUST Cricket Team} 
& Sep 2023 -- May 2024 \\
\multicolumn{2}{@{}X@{}}{Represented NUST in inter-university games and tournaments.} \\
\end{tabularx}







%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------




\vfill
% \center{\footnotesize Last updated: \today}

\end{document}
